Predictive Regressions with Persistent Regressors

### 2019-09-07 paper.tex
ADD empirical results rep

\documentclass{article}
\usepackage{amsmath}
\usepackage{mathrsfs}  
\usepackage{float}
\usepackage{varioref}
\usepackage[margin=1.5in]{geometry}
\title{Predictive Regressions with Persistent Regressors}
\author{Jan Philipp Wöltjen  \\
	Seminar in Statistics CAU Kiel  \\
	}

@@

\subsection{Implementation of the feasible Q-test}

@@

In the CCC-GARCH modsel it has been assumed that there are no volatility transmissions between the returns and the regressor. This assumption seems unrealistic and it reduces the correlation between the residuals as demonstrated by $\hat{\delta}$. There are various multivariate GARCH models suited for incorporating spill-over effects such as the BEKK model of Engle and Kroner (1995). It seems plausible, though, that the variances of both the regressor and the returns share a common stochastic trend which may be imagined as the overall economic uncertainty. This seems reasonable since it is hard to imagine having high variance in returns without having high variance in valuation ratios and vice versa. Simulation is performed similar as in the CCC-GARCH model but now $h_{1, t} =h_{2, t}$ in equation ($\ref{eqn:40}$). Results in Table~\vref{tab:cst-garch} compared with Table~\vref{tab:cy}  indicate that the one-sided Bonferroni Q-test tends to over-reject the true null if innovations are modeled as described above.
\begin{table}[hbt]
\centering
\caption{Finite-sample rejection rates of the true null for right-tailed [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with the variances of innovations sharing a common stochastic trend which is modeled as a univariate GARCH(1, 1) process (10,000 Monte Carlo samples). }
\label{tab:cst-garch}
\begin{tabular}{rrrrrrrrrr}
  \hline
  & Obs & $c$ & $\rho$ & $\delta$ & $\alpha_{_{GARCH}}$ & $\beta_{_{GARCH}}$ & t-test &BQ& BQ$_{{2sided}}$ \\ 
  \hline
1 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.90 & 0.2815 & 0.0952 & 0.0990 \\ 
  2 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.80 & 0.2762 & 0.1009 & 0.1048 \\ 
  3 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.50 & 0.2706 & 0.0942 & 0.0977 \\ 
  4 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.40 & 0.2676 & 0.0961 & 0.1004 \\ 
  5 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.30 & 0.2628 & 0.0932 & 0.0972 \\ 
  6 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.20 & 0.2704 & 0.0908 & 0.0943 \\ 
  7 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.10 & 0.2677 & 0.0935 & 0.0984 \\ 
  8 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.90 & 0.3135 & 0.0733 & 0.0771 \\ 
  9 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.80 & 0.2812 & 0.0703 & 0.0771 \\ 
  10 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.50 & 0.2780 & 0.0683 & 0.0747 \\ 
  11 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.40 & 0.2797 & 0.0676 & 0.0742 \\ 
  12 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.30 & 0.2758 & 0.0664 & 0.0734 \\ 
  13 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.20 & 0.2746 & 0.0629 & 0.0703 \\ 
  14 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.10 & 0.2749 & 0.0656 & 0.0715 \\ 
   \hline
\end{tabular}
\end{table}

\begin{thebibliography}{}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{mathrsfs}  
\usepackage{float}
\usepackage{varioref}
\usepackage[margin=1.5in]{geometry}
\usepackage[flushleft]{threeparttable}
\title{Predictive Regressions with Persistent Regressors}
\author{Jan Philipp Wöltjen  \\
	Seminar in Statistics CAU Kiel  \\
	}

@@

\subsection{Implementation of the feasible Q-test}
\label{implementation}

@@

In the CCC-GARCH model it has been assumed that there are no volatility transmissions between the returns and the regressor. This assumption seems unrealistic and it reduces the correlation between the residuals as demonstrated by $\hat{\delta}$. There are various multivariate GARCH models suited for incorporating spill-over effects such as the BEKK model of Engle and Kroner (1995). It seems plausible, though, that the variances of both the regressor and the returns share a common stochastic trend which may be imagined as the overall economic uncertainty. This seems reasonable since it is hard to imagine having high variance in returns without having high variance in valuation ratios and vice versa. Simulation is performed similar as in the CCC-GARCH model but now $h_{1, t} =h_{2, t}$ in equation ($\ref{eqn:40}$). Results in Table~\vref{tab:cst-garch} compared with Table~\vref{tab:cy}  indicate that the one-sided Bonferroni Q-test tends to over-reject the true null if innovations are modeled as described above.
\begin{table}[hbt]
\centering
\caption{Finite-sample rejection rates of the true null for right-tailed [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with the variances of innovations sharing a common stochastic trend which is modeled as a univariate GARCH(1, 1) process (10,000 Monte Carlo samples). }
\label{tab:cst-garch}
\begin{tabular}{rrrrrrrrrr}
  \hline
  & Obs & $c$ & $\rho$ & $\delta$ & $\alpha_{_{GARCH}}$ & $\beta_{_{GARCH}}$ & t-test &BQ& BQ$_{{2sided}}$ \\ 
  \hline
1 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.90 & 0.2815 & 0.0952 & 0.0990 \\ 
  2 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.80 & 0.2762 & 0.1009 & 0.1048 \\ 
  3 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.50 & 0.2706 & 0.0942 & 0.0977 \\ 
  4 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.40 & 0.2676 & 0.0961 & 0.1004 \\ 
  5 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.30 & 0.2628 & 0.0932 & 0.0972 \\ 
  6 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.20 & 0.2704 & 0.0908 & 0.0943 \\ 
  7 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.10 & 0.2677 & 0.0935 & 0.0984 \\ 
  8 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.90 & 0.3135 & 0.0733 & 0.0771 \\ 
  9 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.80 & 0.2812 & 0.0703 & 0.0771 \\ 
  10 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.50 & 0.2780 & 0.0683 & 0.0747 \\ 
  11 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.40 & 0.2797 & 0.0676 & 0.0742 \\ 
  12 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.30 & 0.2758 & 0.0664 & 0.0734 \\ 
  13 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.20 & 0.2746 & 0.0629 & 0.0703 \\ 
  14 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.10 & 0.2749 & 0.0656 & 0.0715 \\ 
   \hline
\end{tabular}
\end{table}

\section{Empirical Results}

Table~\vref{tab:cy_sp} replicates the key results of Tables 4 and 5 of Campbell and Yogo (2005). The Bonferroni Q-test is implemented as described in section $\ref{implementation}$. Apart from rounding errors, the results are nearly the same except for the following discrepancies. First, the DF-GLS statistics for $p>1$ are higher than reported by Campbell and Yogo (2005).  As previously mentioned, the DF-GLS implementation of section $\ref{implementation}$ was verified with a different open-source implementation. Second, based on the BIC, a lower $p$ of 1 was selected for monthly ldp. Investigations showed that the difference in BIC when $p=1$ compared with $p=2$ is very small. 
%Obtained from https://sites.google.com/site/motohiroyogo/home/publications/Predict_ Data.xls.
\begin{table}[ht]
\centering

\caption{Replicated model parameters from Campbell and Yogo (2005)}
\label{tab:cy_sp}
\begin{threeparttable}
\begin{tabular}{llrrlrrrrrl}
  \hline
dataset & $x$ & obs & $\hat{\delta}$ & $CI_{\rho}$ & DF-GLS & $p$ &t-stat & pt & $\hat{\beta}$ & $CI_{\beta}$ \\ 
  \hline
  SP\_A & lep & 123 & -0.96 & [0.786,0.931] & -2.888 & 1 & 2.76 & 0 & 0.127 & [0.043,0.225] \\ 
  SP\_A & ldp & 123 & -0.85 & [0.94,1.006] & -1.247 & 3 & 1.95 & 0 & 0.083 & [-0.024,0.136] \\ 
  CRSP\_A & lep & 77 & -0.96 & [0.778,0.96] & -2.229 & 1 & 2.77 & 0 & 0.162 & [0.04,0.273] \\ 
  CRSP\_A & ldp & 77 & -0.72 & [0.926,1.01] & -1.033 & 1 & 2.53 & 0 & 0.158 & [0.013,0.186] \\ 
  CRSP\_Q & lep & 305 & -0.99 & [0.944,0.992] & -2.191 & 1 & 2.91 & 0 & 0.047 & [0.011,0.066] \\ 
  CRSP\_Q & ldp & 305 & -0.94 & [0.962,0.999] & -1.696 & 1 & 2.06 & 0 & 0.034 & [-0.009,0.044] \\ 
  CRSP\_M & lep & 913 & -0.99 & [0.985,1] & -1.859 & 1 & 2.66 & 0 & 0.013 & [0.001,0.018] \\ 
  CRSP\_M & ldp & 913 & -0.95 & [0.99,1.001] & -1.433 & 1 & 1.70 & 0 & 0.008 & [-0.005,0.01] \\ 
\hline
\end{tabular}
 \begin{tablenotes}
\item Data is taken from Motohiro Yogo's website at https://drive.google.com/file/d/0BzR-ojpYuaFMcnZteHFyWUVIUFU/view. The regressor is the 10-year moving average earnings to current price ratio [lep] and the log dividend to price ratio [ldp] in logs. 
\end{tablenotes}
\end{threeparttable}
\end{table}

 \pagebreak
\begin{thebibliography}{}
